### 2019-03-11 manuscript/discussion.tex
minor edits across everything, added ideas to discussion for Boris

%B:  at least two surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.
We investigated the individual and joint effects of ploidy and breeding system states in diversification of Solanaceae.
Most significantly, we found that the effects of ploidy, inferred as significant when it is the only trait under consideration, are trumped by breeding systems when the two traits are considered jointly.  % E: is "trumped" too much like gloating?
Interestingly, the difference in diversification rates between the diploids and polyploids is negligible on the background of self-compatibility.
%B: should we mention here that the hidden states presage these results in each case? Maybe we don't want to make too much of that, but it is fairly interesting. Also possibly hit that in your paragraph(s), below.
In the same vein, we recovered a smaller difference in diversification rates between self-incompatible and self-compatible lineages against diploid genomic background. %B: "in diploids" may work better?
%B: need help with pathway single-sentence summary
Motivated by the widespread findings of paleopolyploid ancestry across angiosperms, we also examined support for diploidization in the history of the family, which appears to be weak. %B: "mixed" "not strong" what's the right word here?  E: not "weak", maybe "not strong" or "not nearly as strong as anything else"
Disentangling the patterns of diversification linked to multiple traits is difficult, but our strategy allows tests of complex hypotheses regarding a heterogenous diversification process.
Below, we discuss these key findings and outline a broad approach for application of phylogenetic comparative methods in the context of interactions among traits and diversification process.

% - value of approach
Disentangling the patterns of diversification linked to  multiple traits allowed us the opportunity to model and test complex hypotheses about the heterogenous diversification process in Solanaceae.
Species are created and go extinct based on multiple and often highly correlated phenotypes. However, estimating the speciation and extinction rates remains challenging. Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as disscussed in  \citet{rabosky_2010, beaulieu_2015}),but also, a problem of inadequate model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focus trait first used to model diversification. We presented a roadmap with a series of analyses that can help scientists to identify if an unknown or unobservable trait is worth pursuing. By carefully aggregating and curating ploidy and breeding system data for Solanaceae, we showed how  the complex interaction between ploidy and breeding system  can lead to diversification conclusions that differ from the diversification conclusions of models that focus on one trait at a time.

@@

Diploidization is widely considered to be relatively rare, compared with polyploidization, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history. %cite
As a consequence, it is possible that nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would clearly underestimate the rate of transitions from polyploids to diploids, and would likely cause inflated net diversification rates for diploids. % E: first clause seems like a tautology? second clause does not seem obvious, but could at least say that it could affect div rate estimates
We find weak support for inclusion of diploidization. %cite fig and expand (FIXME).

@@

>>>>

%B:  at least two surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.
We investigated the individual and joint effects of ploidy and breeding system states in diversification of Solanaceae.
Most significantly, we found that the effects of ploidy, inferred as significant when it is the only trait under consideration, are trumped by hidden states and or/ breeding system when added to models.  % E: is "trumped" too much like gloating? - R-Haha
%R- I added hidden states because that hasn't been discussed ever in polyploidy
Interestingly, the difference in diversification rates between the diploids and polyploids is negligible on the background of self-compatibility.
%B: should we mention here that the hidden states presage these results in each case? Maybe we don't want to make too much of that, but it is fairly interesting. Also possibly hit that in your paragraph(s), below.
In the same vein, we recovered a smaller difference in diversification rates between self-incompatible and self-compatible lineages against diploid genomic background. %B: "in diploids" may work better?
%B: need help with pathway single-sentence summary
Motivated by the widespread findings of paleopolyploid ancestry across angiosperms, we also examined support for diploidization in the history of the family, which appears to be weak. %B: "mixed" "not strong" what's the right word here?  E: not "weak", maybe "not strong" or "not nearly as strong as anything else"
Disentangling the patterns of diversification linked to multiple traits is difficult, but our strategy allows tests of complex hypotheses regarding a heterogenous diversification process.
Below, we discuss these key findings and outline a broad approach for application of phylogenetic comparative methods in the context of interactions among traits and diversification process.

% - value of approach
Disentangling the patterns of diversification linked to  multiple traits allowed us the opportunity to model and test complex hypotheses about the heterogenous diversification process in Solanaceae.
Species are created and go extinct based on multiple and often highly correlated phenotypes. However, estimating the speciation and extinction rates remains challenging.

By carefully aggregating and curating ploidy and breeding system data for Solanaceae, we showed how  the complex interaction between ploidy and breeding system  can lead to diversification conclusions that differ from the diversification conclusions of models that focus on one trait at a time.

@@

Diploidization is widely considered to be relatively rare, compared with polyploidization, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history. %cite
As a consequence, it is possible that nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would clearly underestimate the rate of transitions from polyploids to diploids, and would likely cause inflated net diversification rates for diploids. % E: first clause seems like a tautology? second clause does not seem obvious, but could at least say that it could affect div rate estimates
We find strong support in models that included diploidization \cref{table:bayesfactors}. However, estimating the rate at which it occurs based on ploidy level classifications is hard and highly uncertain (see parameter $\delta$ in \cref{suppfigure:DP,suppfigure:DPAB,suppfigure:IDCDCP,suppfigure:IDCDCPAB}) and can change the pattern of ancestral reconstructions (\cref{suppfigure:DPnodipasr,suppfigure:DPasr,suppfigure:DPnodipABasr,suppfigure:DPABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPasr,suppfigure:IDCDCPnodipABasr,suppfigure:IDCDCPABasr}).
%We find weak support for inclusion of diploidization. %cite fig and expand (FIXME).
% R- I corrected the above phrase, we found strong support for the inclusion of diploidization, models that have it are always preferred over models that don't however that parameter is hard to estimate

@@

% R-Here I copied the limitations of the models idea but needs to be reorganized to be cohesive % Fix this a lot more please
% This is the idea on how thorough analyses should be done.
Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as disscussed in  \citet{rabosky_2010, beaulieu_2015}),but also, a problem of inadequate  ``*SSE'' model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focus trait first used to model diversification. We presented a roadmap with a series of analyses that can help scientists to identify if an unknown or unobservable trait is worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  If that is the case on a system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process. When considering  a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE might also suffer from hight type I errors considering more heterogeneity using a hidden state model on top of the multistate SSE is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.

### 2019-03-11 manuscript/introduction.tex
minor edits across everything, added ideas to discussion for Boris

Whole genome duplication (WGD) is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
The widespread prevalence of variation in ploidy has long been considered a salient feature of flowering plant lineages \citep{stebbins1938}. 
WGDs have the potential to affect many phentoypes and a variety of evolutionary \citep{ramsey_2002} and ecological processes \citep{sessa_2019}.
Polyploids have been thought to have lower rates of net diversification rate than diploids \citep{mayrose_2011, mayrose_2015}. 
Recent studies, however, find common and numerous paleo-polyploidizations, including some preceding the emergence of highly diverse plant clades \citep{soltis_2014, landis_2018}, suggesting that WGDs have played an important macroevolutionary role driving innovation and diversification in plants.
Evidence of paleo-polyploidy within the genomes of diploid extant plants also implies the pervasiveness of diploidization, the return of polyploids to the diploid state, throughout the angiosperm phylogeny \citep{soltis_2015, dodsworth_2015}.
% Testing for the presence of diploidization in the context of diversification is important because the presence of a positive net diversification rate for diploids can be the result of an ancestrally polyploid lineage.
% Under this scenario, polyploidy would no longer be considered to reliably slow down diversification, but instead, polyploidy would be the initiator of the diversification process. %B: I think this should read "...polyploidy is no longer be considered an evolutionary dead end."  %R- This last phrase is from Itay and I rather like it. <-- %B: Hmm. But how would it be considered an "initiator of the diversification process?" It seems to be associated with lower diversification. In other words, I also agree with both %R and Itay, but not with what the current phrasing is asserting.
% E: I wrote the two sentences below to try to reconcile the text and comments below.  But then I realized we don't actually test this hypothesis.
% One hypothesis is that diploids have a higher net diversification rate if they were ancestrally polyploid than if they had no polyploid ancestry.
% Testing this hypothesis requires incorporating diploidization in analyses of diversification.
% E: so try again -- okay?
This could affect interpretation of different net diversification rates for diploids and polyploids, especially if diploids have a higher net diversification rate if they were ancestrally polyploid than if they had no polyploid ancestry.

@@

Two recent methodological developments enable disentangling the complex interactions between two or more traits and diversification.
First, \citet{fitzjohn_2012} extended the state-dependent diversification ``*SSE'' modeling framework \citep{maddison_2007} to allow estimating the effect of an arbitrary number of states (enabling multi-state, MuSSE, instead of binary state, BiSSE, speciation and extinction models).
This allows multiple states to represent trait combinations, particularly useful if one is interested in explicitly testing whether combinations of traits non-additively affect speciation or extinction. 
Second, \citet{beaulieu_2016}  proposed an extension of the *SSE framework by introducing a model with unspecified, or `hidden' traits (HiSSE model), which can affect the diversification process.
Because variation in speciation and extinction rates may not be due solely to the focal trait, HiSSE simultaneously enables hidden states to explain such variation, and it reduces the elevated false-positive error rates \citep{rabosky_2017}.
%B: This may be a good portion of Discussion--faults and qualities of methods?
%HiSSE models have effectively shown that some traits associated with diversification in BiSSE analyses are actually not associated with the diversification process, and instead a hidden state is linked to differences in the diversification rate.  
%Such results raise the question of the identity of the hidden state, or whether it is an approximation of some unknowable heterogeneity, as well as whether interactions between the known and hidden trait were modeled appropriately. 
%Third, one can simultaneously consider the effects of multiple known traits using MuSSE, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
%However, MuSSE might also suffer from hight type I errors if there are other processes shaping diversification other than the traits observed \citep{caetano_2018}
%Therefore, a fourth option exists: considering both the presence of multiple known traits  linked to the diversification process, but also, some unknown or hidden state changing speciation and extinction rates. 
A joint application of these advances allows simultaneous consideration of the effects of multiple known traits on the diversification process, along with the presence of other unobserved states that can affect speciation and extinction rates. 
%These four modeling strategies are proposed here in the context of studying complex interactions among traits, linked diversification.

@@

>>>>

Polyploidy, the acquisition of extra sets of chromosomes, is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
%R- Polyploid people are careful at not using interchangeably WGD so I switched back to polyploidy terminology. Since we are not using anything molecular I'd rather keep it as polyploidy
The widespread prevalence of variation in ploidy has long been considered a salient feature of flowering plant lineages \citep{stebbins1938}. 
Polyploidy events have the potential to affect many phentoypes and a variety of evolutionary \citep{ramsey_2002} and ecological processes \citep{sessa_2019}.
Polyploids have been thought to have lower rates of net diversification rate than diploids \citep{mayrose_2011, mayrose_2015}. 
Recent studies, however, find common and numerous paleo-polyploidizations, including some preceding the emergence of highly diverse plant clades \citep{soltis_2014, landis_2018}, suggesting that polyploidy events have played an important macroevolutionary role driving innovation and diversification in plants.
Evidence of paleo-polyploidy within the genomes of diploid extant plants also implies the pervasiveness of diploidization, the return of polyploids to the diploid state, throughout the angiosperm phylogeny \citep{soltis_2015, dodsworth_2015}.
% Testing for the presence of diploidization in the context of diversification is important because the presence of a positive net diversification rate for diploids can be the result of an ancestrally polyploid lineage.
% Under this scenario, polyploidy would no longer be considered to reliably slow down diversification, but instead, polyploidy would be the initiator of the diversification process. %B: I think this should read "...polyploidy is no longer be considered an evolutionary dead end."  %R- This last phrase is from Itay and I rather like it. <-- %B: Hmm. But how would it be considered an "initiator of the diversification process?" It seems to be associated with lower diversification. In other words, I also agree with both %R and Itay, but not with what the current phrasing is asserting.
% E: I wrote the two sentences below to try to reconcile the text and comments below.  But then I realized we don't actually test this hypothesis.
% One hypothesis is that diploids have a higher net diversification rate if they were ancestrally polyploid than if they had no polyploid ancestry.
% Testing this hypothesis requires incorporating diploidization in analyses of diversification.
% E: so try again -- okay? 
%R- yup- good resolution
This could affect interpretation of different net diversification rates for diploids and polyploids, especially if diploids have a higher net diversification rate if they were ancestrally polyploid than if they had no polyploid ancestry.

@@

Two recent methodological developments enable disentangling the complex interactions between two or more traits and diversification.
First, \citet{fitzjohn_2012} extended the state-dependent diversification ``*SSE'' modeling framework \citep{maddison_2007} to allow estimating the effect of an arbitrary number of states (enabling multi-state, MuSSE, instead of binary state, BiSSE, speciation and extinction models).
This allows multiple states to represent trait combinations, particularly useful if one is interested in explicitly testing whether combinations of traits non-additively affect speciation or extinction. 
Second, \citet{beaulieu_2016}  proposed an extension of the *SSE framework by introducing a model with unspecified, or `hidden' traits (HiSSE model), which can affect the diversification process.
Because variation in speciation and extinction rates may not be due solely to the focal trait, HiSSE simultaneously enables hidden states to explain such variation, and it reduces the elevated false-positive error rates.
%B: This may be a good portion of Discussion--faults and qualities of methods?
%HiSSE models have effectively shown that some traits associated with diversification in BiSSE analyses are actually not associated with the diversification process, and instead a hidden state is linked to differences in the diversification rate.  
%Such results raise the question of the identity of the hidden state, or whether it is an approximation of some unknowable heterogeneity, as well as whether interactions between the known and hidden trait were modeled appropriately. 
%Third, one can simultaneously consider the effects of multiple known traits using MuSSE, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
%However, MuSSE might also suffer from hight type I errors if there are other processes shaping diversification other than the traits observed \citep{caetano_2018}
%Therefore, a fourth option exists: considering both the presence of multiple known traits  linked to the diversification process, but also, some unknown or hidden state changing speciation and extinction rates. 
A joint application of these advances allows simultaneous consideration of the effects of multiple known traits on the diversification process, along with the presence of other unobserved states that can affect speciation and extinction rates. 
%These four modeling strategies are proposed here in the context of studying complex interactions among traits, linked diversification.

@@

% R- I'm good with this intro. It is simple and reads well.

### 2019-03-11 manuscript/methods.tex
minor edits across everything, added ideas to discussion for Boris

Matching our character state data to the largest time-calibrated phylogeny of Solanaceae \citep{sarkinen_2013} yielded 595 species with ploidy and/or breeding system information on the tree.
Binary or three-state classification of ploidy and breeding system for the 595 taxa is summarized in \cref{figure:stateclassifications}.
We retained all of these species in each of the analyses below because pruning away tips lacking breeding system in the ploidy-only analyses (and vice versa) would discard data that could inform the diversification models.
A total of 405 taxa without any information about breeding system or polyploidy were excluded.
%Tips without trait data might not improve point estimation of diversification parameters while increasing uncertainty in the estimates of trait linked diversification
% R-This is very important but I have removed it because I think it is a full on paper by its own
Including this many more species would have prohibitively slowed our analyses, especially those implementing the most complex models.

@@

In order to investigate the association between ploidy level and diversification, we first defined a binary state speciation and extinction model (BiSSE, \citealt{maddison_2007}) in which taxa were classified as diploid (D) or polyploid (P).
We call this the D/P ploidy model.
The model parameters are speciation rates ($\lambda_D$, $\lambda_P$) and extinction rates ($\mu_D$, $\mu_P$) for each state, and a rate of transition from D to P ($\rho$).

@@

The ID/CD/CP model could also suffer from a high type I error, just like a two state BiSSE model. 
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018,  huang_2018}.
We refer to this as the ID/CD/CP+A/B model.
A fully parameterized version of this model would have 26 rate parameters. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fit a simplified version with 15 parameters.
The reduction in parameter space was achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\ \rho_C,\ \delta,\ q_{IC}$ as defined for the ID/CD/CP model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},\ \lambda_{ID_B},\ \lambda_{CD_A},\ \lambda_{CD_B},\ \lambda_{CP_A},\ \lambda_{CP_B},\ \mu_{ID_A},\ \mu_{ID_B},\ \mu_{CD_A},\ \mu_{CD_B},\ \mu_{CP_A},\ \mu_{CP_B}$).
%B: I can't tell, but it seems to me that this 26->16 parameter reduction makes it possible to underestimate the effect of these hidden states.Perhaps this complication is covered in the Discussion section. 
%R- It is possible, but adding all the parameters can also result in an underestimation of the hidden states contribution because it is not enough sample to accurately estimate transitions. In my simulations for diversification-free models, accurately estimating 10 parameters can only be achieved with trees with more than 500 tips. Because of that experience I think 16 parameters is already pushing really the inference machine hard. This happens because the phylogeny is not an independent sample so your ESS is much much smaller and you might end up over-parameterizing.

@@

For the models with ploidy changes, we allowed diploidization by adding a parameter $\delta$ for transitions from P back to D (in the D/P and D/P+A/B models) or from CP back to CD (in the I/C and I/C+A/B models).
We did not allow transitions from CP back to ID because that would include regain of SI.
The models are denoted with $+\delta$ in \cref{table:marginallike}.
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level (see Supplementary Information). % (data available at https://www.github.com/roszenil/solploidy/datasets).
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we fit models with and without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a process can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the most essential process to understand the interactions among polyploidy, breeding system, and diversification.

@@

Using the marginal likelihood values, we calculated thirteen different Bayes factors.
Six compared the models of ploidy against one other (D/P and D/P+A/B, each with or without diploidization), one compared the breeding system models (I/C and I/C+A/B), and six compared the models with both traits (ID/CD/CP and ID/CD/CP+A/B, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In mathematical terms, the D/P, I/C, and ID/CD/CP state spaces are not `lumpable' with respect to one another \citep{tarasov_2019}.
% E: I think this short explanation is clear enough, especially with the figure.  I'm not sure whether the hierarchical concept is exactly applicable here.
%R: Boris in the introduction mentions this possible causal relationship would that be equivalent to say hierarchical?
Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $BF(M_0,\ M_1) = \ln[ P(\mathbf{X} | M_0) - P(\mathbf{X} | M_1]$.
There is `positive' support for $M_0$ when this value is more than 2, `strong' support when it is more than 6, and `very strong' support when it is more than 10 \citep{kass1995}.

>>>>

Matching our character state data to the largest time-calibrated phylogeny of Solanaceae \citep{sarkinen_2013} yielded 595 species with ploidy and/or breeding system information on the tree.
Binary or three-state classification of ploidy and breeding system for the 595 taxa is summarized in \cref{figure:stateclassifications}.
We retained all of these species in each of the analyses below because pruning away tips lacking breeding system in the ploidy-only analyses (and vice versa) would discard data that could inform the diversification models.
A total of 405 taxa without any information about breeding system or polyploidy were excluded.
%Tips without trait data might not improve point estimation of diversification parameters while increasing uncertainty in the estimates of trait linked diversification
% R-This is very important but I have removed it because I think it is a full on paper by its own
%Including this many more species would have prohibitively slowed our analyses, especially those implementing the most complex models.

@@

In order to investigate the association between ploidy level and diversification, we first defined a binary state speciation and extinction model (BiSSE, \citealt{maddison_2007}) in which taxa were classified as diploid (D) or polyploid (P).
We call this the D/P ploidy model.
The model parameters are speciation rates ($\lambda_D$, $\lambda_P$) and extinction rates ($\mu_D$, $\mu_P$) for each state, and a rate of transition from D to P ($\rho$). This is the same model fitted by \citet{mayrose_2011} but applied to the larger Solanaceae dataset.
% R- Itay wanted to hightlight that is the same model. Definitely a BiSSE. He did the ClaSSE later in the 2014 response.

@@

The ID/CD/CP model could also suffer from a high type I error, just like a two state BiSSE model. 
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018,  huang_2018}.
We refer to this as the ID/CD/CP+A/B model.
A fully parameterized version of this model would have 26 rate parameters. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fit a simplified version with 16 parameters. % You were missing counting the alpha
The reduction in parameter space was achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\rho_C,\ q_{IC}$ as defined for the ID/CD/CP model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},  \lambda_{ID_B},  \lambda_{CD_A}, \lambda_{CD_B}, \lambda_{CP_A}, \lambda_{CP_B}, \mu_{ID_A}, \mu_{ID_B}, \mu_{CD_A}, \mu_{CD_B},  \mu_{CP_A}, \mu_{CP_B}$).
%B: I can't tell, but it seems to me that this 26->16 parameter reduction makes it possible to underestimate the effect of these hidden states.Perhaps this complication is covered in the Discussion section. 
%R- It is possible, but adding all the parameters can also result in an underestimation of the hidden states contribution because it is not enough sample to accurately estimate transitions. In my simulations for diversification-free models, accurately estimating 10 parameters can only be achieved with trees with more than 500 tips. Because of that experience I think 16 parameters is already pushing really the inference machine hard. This happens because the phylogeny is not an independent sample so your ESS is much much smaller and you might end up over-parameterizing.

@@

For the models with ploidy changes, we allowed diploidization by adding a parameter $\delta$ for transitions from P back to D (in the D/P and D/P+A/B models) or from CP back to CD (in the I/C and I/C+A/B models).
We did not allow transitions from CP back to ID because that would include regain of SI.
The models are denoted with $+\delta$ in \cref{table:marginallike}.
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level (see \url{https://github.com/roszenil/solploidy} for archived dataset). % (data available at https://www.github.com/roszenil/solploidy/datasets).
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we fit models with and without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a process can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the most essential process to understand the interactions among polyploidy, breeding system, and diversification.

@@

Using the marginal likelihood values, we calculated thirteen different Bayes factors.
Six compared the models of ploidy against one other (D/P and D/P+A/B, each with or without diploidization), one compared the breeding system models (I/C and I/C+A/B), and six compared the models with both traits (ID/CD/CP and ID/CD/CP+A/B, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In mathematical terms, the D/P, I/C, and ID/CD/CP state spaces are not `lumpable' with respect to one another \citep{tarasov_2019}.
% E: I think this short explanation is clear enough, especially with the figure.  I'm not sure whether the hierarchical concept is exactly applicable here.
%R: Boris in the introduction mentions this possible causal relationship would that be equivalent to say hierarchical?
Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $BF(M_0,\ M_1) = \ln[ P(\mathbf{X} | M_0) - P(\mathbf{X} | M_1)]$.
There is `positive' support for $M_0$ when this value is more than 2, `strong' support when it is more than 6, and `very strong' support when it is more than 10 \citep{kass1995}.
